Inefficient Concessions and Mediation

### 2021-02-02 notes.tex
add notes on cse vs grim trigger welfare

\section{No material value CSE vs. repeated game}
Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
						\[
						  \frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g_0 \geq \frac{1}{1-\de_h} (W-D)
						\]
						\[
						  pT + (1-p)(W-D) - (1-\de_h)(1-p) g^0 \geq W-D
						\]
						\[
						  \de_h (1-p) g^0 \geq W-D - pT - (1-p)(W-D) +g^0(1-p)
						\]
						\[
						  \de_h (1-p) g^0 \geq p(W-D-T) +g^0(1-p)
						\]
						\[
						  \de_h \geq \frac{p(W-D-T)}{g^0(1-p)} + 1 = \frac{p(W-D-T)}{p(T+D)(1-p)} + 1 
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} + \frac{(-D-T)}{(T+D)(1-p)} + 1 = \frac{W}{(T+D)(1-p)} - \frac{1}{1-p} + 1
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} - \frac{p}{1-p}
						\]
							\begin{itemize}
								\item For P6 this is zero, for P1 and P2 it's negative, and it's positive for the rest
							\end{itemize}
						The following shows that this is strictly smaller than $\de^h$. \textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
							\begin{itemize}
								\item $T+D>W$
								\item $-(T+D)<-W$
								\item $-p(T+D)<-pW$
								\item $W-p(T+D)<W-pW$
								\item $\frac{W-p(T+D)}{T+D}<\frac{W-pW}{T+D} = \frac{(1-p)W}{T+D}$
								\item $\frac{W-p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p}{1-p}< \frac{W}{T+D}$. Q.E.D.
								\item This is nice, but I'm not sure it helps with the narrative of the story.
									\begin{itemize}
										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
											\begin{itemize}
												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
												\item Should I compare grim trigger welfare to see which is higher?
											\end{itemize}
									\end{itemize}
							\end{itemize}

>>>>

\section{No material value CSE vs. repeated game}
\subsection{Patience threshold}
Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
						\[
						  \frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g_0 \geq \frac{1}{1-\de_h} (W-D)
						\]
						\[
						  pT + (1-p)(W-D) - (1-\de_h)(1-p) g^0 \geq W-D
						\]
						\[
						  \de_h (1-p) g^0 \geq W-D - pT - (1-p)(W-D) +g^0(1-p)
						\]
						\[
						  \de_h (1-p) g^0 \geq p(W-D-T) +g^0(1-p)
						\]
						\[
						  \de_h \geq \frac{p(W-D-T)}{g^0(1-p)} + 1 = \frac{p(W-D-T)}{p(T+D)(1-p)} + 1 
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} + \frac{(-D-T)}{(T+D)(1-p)} + 1 = \frac{W}{(T+D)(1-p)} - \frac{1}{1-p} + 1
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} - \frac{p}{1-p}
						\]
							\begin{itemize}
								\item For P6 this is zero, for P1 and P2 it's negative, and it's positive for the rest
							\end{itemize}
						The following shows that this is strictly smaller than $\de^h$. \textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
							\begin{itemize}
								\item $T+D>W$
								\item $-(T+D)<-W$
								\item $-p(T+D)<-pW$
								\item $W-p(T+D)<W-pW$
								\item $\frac{W-p(T+D)}{T+D}<\frac{W-pW}{T+D} = \frac{(1-p)W}{T+D}$
								\item $\frac{W-p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p}{1-p}< \frac{W}{T+D}$. Q.E.D.
								\item This is nice, but I'm not sure it helps with the narrative of the story.
									\begin{itemize}
										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
											\begin{itemize}
												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
												\item Should I compare grim trigger welfare to see which is higher?
											\end{itemize}
									\end{itemize}
							\end{itemize}

\subsection{Welfare}
Welfare under no material value CSE is always at least as large as welfare under repeated-game grim trigger
\[
  p\frac{T}{1-\de_h} + (1-p)\frac{W-D}{1-\de_h} - p(T+D) \geq p\frac{T}{1-\de_h} + (1-p)\frac{-D}{1-\de_h} + (1-p)\frac{\de_h}{1-\de_h}(W-D)
\]
\[
  (1-p)\frac{W-D}{1-\de_h} - p(T+D) \geq (1-p)\frac{-D}{1-\de_h} + (1-p)\frac{\de_h}{1-\de_h}(W-D)
\]
\[
  (1-p)(W-D) - p(1-\de_h)(T+D) \geq -(1-p)D + (1-p)\de_h(W-D)
\]
\[
  (1-p)W - p(1-\de_h)(T+D) \geq (1-p)\de_h(W-D)
\]
\[
  (1-p)W -(1-p)\de_h(W-D)\geq  p(1-\de_h)(T+D) 
\]
\[
  W-pW - \de_hW+\de_hD +p\de_hW-p\de_hD\geq  pT + pD -p\de_hT - p\de_hD 
\]
\[
  W-pW - \de_hW+\de_hD +p\de_hW \geq  pT + pD -p\de_hT 
\]
\[
  W - \de_hW+\de_hD +p\de_hW \geq  pT + pD + pW -p\de_hT 
\]
Because $T +D > W$, we have 
\[
  W - \de_hW+\de_hD +p\de_hW \geq  pT + pD + pW -p\de_hT > -p\de_hT 
\]
\[
  (1-\de_h)W +\de_hD +p\de_hW + p\de_hT > 0 
\]
Each term on the left is strictly larger than 0, so this statement is always true.
